Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_lncRNA.Rmd
lncRNA - stringtie

```{r, engine='bash'}

wget -r \
--no-directories --no-parent \
-P ../data/lncRNA \
-A "*fastq.gz" https://gannet.fish.washington.edu/Atumefaciens/20230519-E5_coral-fastqc-fastp-multiqc-RNAseq/A_pulchra/trimmed/

@@

curl -O https://gannet.fish.washington.edu/seashell/bu-github/deep-dive/D-Apul/data/Amil/ncbi_dataset/data/GCF_013753865.1/genomic.gtf
```

@@

```{r, engine='bash'}
find ../output/05.33-lncRNA-discovery/*sorted.bam \
| xargs basename -s .sorted.bam | xargs -I{} \
/home/shared/stringtie-2.2.1.Linux_x86_64/stringtie \
-p 16 \
-G ../data/Amil/ncbi_dataset/data/GCF_013753865.1/genomic.gff \
-o ../output/05.33-lncRNA-discovery/{}.gtf \
../output/05.33-lncRNA-discovery/{}.sorted.bam
```

>>>>

```{r, engine='bash'}
wget -r \
--no-directories --no-parent \
-P ../data/lncRNA \
-A "*fastq.gz" https://gannet.fish.washington.edu/Atumefaciens/20230519-E5_coral-fastqc-fastp-multiqc-RNAseq/A_pulchra/trimmed/

@@

@@

```{r, engine='bash'}
find ../output/lncRNA/*sorted.bam \
| xargs basename -s .sorted.bam | xargs -I{} \
/home/shared/stringtie-2.2.1.Linux_x86_64/stringtie \
-p 16 \
-G ../lncRNA/genomic.gff \
-o ../output/lncRNA/{}.gtf \
../output/lncRNA/{}.sorted.bam
```
